04-Data-Analysis

### 2021-04-21 00-Data-Processing/04-Data-Analysis.Rmd
Update wph analysis by TYPE
include the type of food bank in the analysis of wph differences

Join the food bank data to the travel time matrices:
```{r}
ttm_car <- ttm_car %>%
  left_join(foodbank_locations %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            COVIDClose),
            by = c("OBJECTID" = "ID"))

ttm_transit <- ttm_transit %>%
  left_join(foodbank_locations %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            COVIDClose),
            by = c("OBJECTID" = "ID"))

ttm_walk <- ttm_walk %>%
  left_join(foodbank_locations %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            COVIDClose),
            by = c("OBJECTID" = "ID"))
```

@@

### Pre-COVID Scenario

@@

```{r minimum-travel-time-baseline, include=FALSE}
# retrieve minimum travel time for pre-covid locations
min_ttm_car_baseline <- ttm_car %>%
  #dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

min_ttm_transit_baseline <- ttm_transit %>%
  #dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

min_ttm_walk_baseline <- ttm_walk %>%
  #dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

```{r minimum-travel-time-covid, include=FALSE}
# retrieve minimum travel time during covid to sites that didnt close
min_ttm_car_covid <- ttm_car %>%
  dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

min_ttm_transit_covid <- ttm_transit %>%
  dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

min_ttm_walk_covid <- ttm_walk %>%
  dplyr::filter(COVIDClose == "No") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

```{r}
min_ttm_d <- min_ttm_baseline_taz %>% 
  left_join(min_ttm_covid_taz %>%
              st_drop_geometry() %>%
              transmute(TAZUID,
                        wph_children_covid = wph_children,
                        wph_adults_covid = wph_adults,
                        wph_seniors_covid = wph_seniors), 
            by = "TAZUID") %>%
  mutate(wph_children_d = wph_children_covid / wph_children - 1,
         wph_adults_d = wph_adults_covid / wph_adults - 1,
         wph_seniors_d = wph_seniors_covid / wph_seniors - 1)

>>>>

Join the food bank data to the travel time matrices:
```{r}
ttm_car <- ttm_car %>%
  left_join(foodbank_locations %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            TYPE,
                            COVIDClose),
            by = c("OBJECTID" = "ID"))

ttm_transit <- ttm_transit %>%
  left_join(foodbank_locations %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            TYPE,
                            COVIDClose),
            by = c("OBJECTID" = "ID"))

ttm_walk <- ttm_walk %>%
  left_join(foodbank_locations %>%
              st_drop_geometry() %>%
              dplyr::select(ID,
                            TYPE,
                            COVIDClose),
            by = c("OBJECTID" = "ID"))
```

@@

### Pre-COVID Scenario to Meal Services

@@

```{r minimum-travel-time-baseline, include=FALSE}
# retrieve minimum travel time for pre-covid locations
min_ttm_car_baseline <- ttm_car %>%
  #dplyr::filter(COVIDClose == "No") %>%
  filter(TYPE != "Food Banks") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

min_ttm_transit_baseline <- ttm_transit %>%
  #dplyr::filter(COVIDClose == "No") %>%
  filter(TYPE != "Food Banks") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

min_ttm_walk_baseline <- ttm_walk %>%
  #dplyr::filter(COVIDClose == "No") %>%
  filter(TYPE != "Food Banks") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

```{r minimum-travel-time-covid, include=FALSE}
# retrieve minimum travel time during covid to sites that didnt close
min_ttm_car_covid <- ttm_car %>%
  dplyr::filter(COVIDClose == "No", TYPE != "Food Banks") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

min_ttm_transit_covid <- ttm_transit %>%
  dplyr::filter(COVIDClose == "No", TYPE != "Food Banks") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

min_ttm_walk_covid <- ttm_walk %>%
  dplyr::filter(COVIDClose == "No", TYPE != "Food Banks") %>%
  group_by(UID) %>%
  summarize(travel_time = min(travel_time),
            DAUID = first(DAUID),
            TAZUID = first(TAZUID),
            p_car = first(p_car),
            p_transit = first(p_transit),
            p_walk = first(p_walk),
            children = first(children),
            adults = first(adults),
            seniors = first(seniors),
            .groups = "drop") %>%

@@

```{r}
min_ttm_d <- min_ttm_baseline_taz %>% 
  left_join(min_ttm_covid_taz %>%
              st_drop_geometry() %>%
              transmute(TAZUID,
                        wph_children_covid = wph_children,
                        wph_adults_covid = wph_adults,
                        wph_seniors_covid = wph_seniors), 
            by = "TAZUID") %>%
  mutate(wph_children_d = wph_children_covid / wph_children - 1,
         wph_children_d = replace_na(wph_children_d, 0),
         wph_adults_d = wph_adults_covid / wph_adults - 1,
         wph_adults_d = replace_na(wph_adults_d, 0),
         wph_seniors_d = wph_seniors_covid / wph_seniors - 1,
         wph_seniors_d = replace_na(wph_seniors_d, 0))
